API Evolution: A Study of Software Stability and Change Trends

### 2013-10-08 apie-2013/paper.tex
APIE new methodology formula for new ratio calculation.

Once the release dates were collected we set about analyzing out data by creating change ratios surrounding the release dates of each project as a way to measure
the trend of a particular change type. 
To do this we used Equation~\ref{eq:norm}. Equation~\ref{eq:norm} works by summing a particular change type in commits ($T_c$)
from the release date ($r$) to a given number of days after the release ($d$) divided by the number of commits in this date range ($|c|$), then dividing
this by the sum of that same particular change type in commits($T_c$) from a given number of days ($d$) before the release date ($r$) to
the release date divided by divided by the number of commits in this date range ($|c|$). 
This equation gives us a ratio of a particular change type happening before and after a particular release. If the ratio is above 1 then that particular change
type occurs more frequently after the release and if it is below 1 then is occurs more frequently before the release. For the purposes of our study, we set the
number of days before and after the release ($d$) to 60 as the projects studies had many months in between their major releases. This quantitative data
formed much of the basis for the results to come in Section~\ref{sec:results}

\begin{equation}
\text{Ratio}_{norm} = \frac{ \sum_{c=r}^{r+d} T_c / |c|} { \sum_{c=r}^{r-d} T_c / |c|}
\label{eq:norm}
\end{equation}

>>>>

Once the release dates were collected we set about analyzing out data by creating average change ratios surrounding the release dates of each 
project as a way to measure the trend of a particular change type at a release type. 
To do this we used Equation~\ref{eq:norm}. Equation~\ref{eq:norm} works to create a change ratio by first creating a numerator by summing across all releases of
a given release type a sum of a particular change type in commits ($T_c$)
from the release date ($r$) to a given number of days after the release ($d$) divided by the number of commits in this date range ($|c|$). Next the denominator
is created by summing across all release of a given release type
a sum of that same particular change type in commits($T_c$) from a given number of days ($d$) before the release date ($r$) to
the release date divided by divided by the number of commits in this date range ($|c|$). This numerator and denominator form the final change ratio.
This equation gives us a ratio of a particular change type happening before and after a particular release. If the ratio is above 1 then that particular change
type occurs more frequently after the release and if it is below 1 then is occurs more frequently before the release. For the purposes of our study, we set the
number of days before and after the release ($d$) to 60 as the projects studies had many months in between their major releases. This quantitative data
formed much of the basis for the results to come in Section~\ref{sec:results}

\begin{equation}
\text{ChangeRatio} = \frac{ \sum_{r_0}^{r_n}\sum_{c=r}^{r+d} T_c / |c|} { \sum_{r_0}\sum_{c=r}^{r-d} T_c / |c|}
\label{eq:norm}
\end{equation}
